---
title: "Introduction to classiccompare"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to classiccompare}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(classiccompare)
```

## Basic comparison

`classic_compare()` compares two data frames the way SAS's PROC COMPARE
compares two datasets. With no `id` or `by`, observations are matched by
row position:

```{r}
base <- data.frame(id = c("A", "B", "C"), x = c(1, 2, 3), y = c("a", "b", "c"))
comp <- data.frame(id = c("C", "A", "D"), x = c(3, 1.5, 9), y = c("c", "a", "d"))

classic_compare(base, comp)
```

## Matching by ID

Supplying `id` matches observations by key value instead of position, so
row order and dropped/added rows don't produce misleading results:

```{r}
classic_compare(base, comp, id = "id", listall = TRUE)
```

## Tolerance-based comparison

```{r}
classic_compare(data.frame(x = 100), data.frame(x = 100.4),
                method = "percent", criterion = 0.5)
```

## Return code for QC scripts

```{r}
res <- classic_compare(base, comp, id = "id")
sysinfo(res)
sysinfo_decode(sysinfo(res))
```

```{r}
stopifnot_example <- tryCatch(
  stopifnot(sysinfo(res) == 0L),
  error = function(e) "datasets differ — this would normally halt a QC script"
)
stopifnot_example
```

## Comparing only specific variables

```{r}
classic_compare(base, comp, id = "id", var = "x")
```

## Structure-only comparison

```{r}
classic_compare(base, comp, id = "id", novalues = TRUE, listall = TRUE)
```